Figure 3c

### 2018-05-16 inst/figure3c/figure3c.Rmd
adding supp 5a-b Rmds and photos

>>>>

_Example confluence measurment_

```{r, out.width = "850px"}

url <- fileMap(type = "png")["Supplementary Figure 5a"][[1]]
knitr::include_graphics(file.path(projectUrl, url))

<div class = "caption">
Representative pictures from the growth analysis shown in Figure 3C. The green color indicates the surface covered by cells as detected by the analysis software.
</div>

_Example phase contrast_

```{r, out.width = "850px"}

url <- fileMap(type = "png")["Supplementary Figure 5b"][[1]]
knitr::include_graphics(file.path(projectUrl, url))

<div class = "caption">
A representative phase contrast picture from the 12 hour time point of the growth analysis in Figure 3C.
</div>
